### 2019-12-15 frontmatter.tex
switched paper 2 with 3

%-------------------------------------------------------------------------------
% Dedication (comment if none)
%-------------------------------------------------------------------------------
%
\dedication{
	{\it If the scientist had an infinity of time at his disposal, it would be sufficient to say to him, ``Look, and look carefully.''}\\[20pt]
	Henri Poincar\'e
}

@@

  \conferenceitem%
    {\underline{Z. Ge}, L. Brandt}% Authors
    {2016}% Year
    {Simulation of the self-assembly of colloidal particles in a microchannel}% Title
    {7th Summer school of Complex Motions in Fluids}% Conference
    {Zenderen, Twente, Netherlands}% Location

>>>>

%-------------------------------------------------------------------------------
% Dedication (comment if none)
%-------------------------------------------------------------------------------
%
\dedication{
	{\it If the scientist had an infinity of time, it would be sufficient to say, \\``Look, and look carefully.''}\\[20pt]
	Henri Poincar\'e
}

@@

  \conferenceitem%
    {\underline{Z. Ge}, L. Brandt}% Authors
    {2016}% Year
    {Simulation of the self-assembly of colloidal particles in a microchannel}% Title
    {7$^{th}$ Summer school of Complex Motions in Fluids}% Conference
    {Zenderen, Twente, Netherlands}% Location

### 2019-12-15 overview.tex
switched paper 2 with 3

%-------------------------------------------------------------------------------
\section{Our Contribution}
%
Our contributions are as follows. We validate that the foremost wireless
algorithm for the understanding of the lookaside buffer by O.  Moore
\cite{cite:0} is maximally efficient. Further, we explore new real-time
methodologies ({Hyp}), which we use to show that the little-known
knowledge-based algorithm for the exploration of the Turing machine by Taylor
et al. \cite{cite:0} runs in
%
\begin{equation}
	\Omega (\log \log \log {n} ^ { \log \log n })
	\label{eq:eq1}
\end{equation}
%
time. This outcome might seem unexpected but has ample historical precedence.

The rest of this paper is organized as follows. Primarily,  we motivate the
need for DNS. On a similar note, we disprove the refinement of 2 bit
architectures.  We place our work in context with the existing work in this
area. Ultimately, we conclude.

@@

%===============================================================================
\chapter{Principles}
%===============================================================================
%

\begin{figure}[htpb]
	\centering
	\includegraphics{dia0}
	\caption{%
	The relationship between our heuristic and the robust unification of
	local-area networks and congestion control.
	}
	\label{fig:introLabel0}
\end{figure}

\begin{equation}
	\mathcal{N} = \nabla\bcdot\boldsymbol{u}
	\label{eq:eq2}
\end{equation}

%-------------------------------------------------------------------------------
\section{Stochastic Technology}
%

%===============================================================================
\chapter{Evaluation}
%===============================================================================
%

%-------------------------------------------------------------------------------
\section{Hardware and Software Configuration}
%
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.7\textwidth]{figure0}
	\caption{%
	The median throughput of Hyp, as a function of bandwidth.
	}
	\label{fig:introLabel2}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.7\textwidth]{figure1}
	\caption{%
	The median sampling rate of Hyp, as a function of energy.
	}
	\label{fig:introLabel3}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.7\textwidth]{figure2}
	\caption{%
	The expected energy of our methodology, compared with the other algorithms.
	}
	\label{fig:introLabel4}
\end{figure}

%-------------------------------------------------------------------------------
\section{Experimental Results}
%
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.7\textwidth]{figure3}
	\caption{
	These results were obtained by Y. Taylor et al. \cite{cite:3}; we reproduce
	them here for clarity. Of course, this is not always the case.
	}
	\label{fig:introLabel5}
\end{figure}

%===============================================================================
\chapter{Related Work}
%===============================================================================
%

@@

%===============================================================================
\chapter{Test chapter, a very very very long title to test the table of contents}
%===============================================================================

This chapter is meant for testing the correct referencing of figures, equations
and tables.

% equations
%
\begin{equation}
	1 + 1 = 2
	\label{eq:test_eq1}
\end{equation}

\begin{align}
	2 + 2 = 4
	\label{eq:test_eq2}
\end{align}

\begin{equation}
	3 + 3 = 6
	\label{eq:test_eq3_intro}
\end{equation}

% tables
%
\begin{table}
	\centering
	\begin{tabular}{c}
		1
	\end{tabular}
	\caption{Test table 1}
	\label{tab:test_tab1}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{c}
		2
	\end{tabular}
	\caption{Test table 2}
	\label{tab:test_tab2}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{c}
		3
	\end{tabular}
	\caption{Test table 3}
	\label{tab:test_tab3_intro}
\end{table}

% figures
%
\begin{figure}[h!]
	\centering
	test figure 1
	\caption{Test figure 1}
	\label{fig:test_fig1}
\end{figure}

\begin{figure}[h!]
	\centering
	test figure 2
	\caption{Test figure 2}
	\label{fig:test_fig2}
\end{figure}

\begin{figure}[h!]
	\centering
	test figure 3
	\caption{Test figure 3}
	\label{fig:test_fig3_intro}
\end{figure}

% test references
%
\hrule
\begin{itemize}
	\item reference to equation 1: \eqref{eq:test_eq1}
	\item reference to equation 2: \eqref{eq:test_eq2}
	\item reference to equation 3: \eqref{eq:test_eq3_intro}
\end{itemize}
\hrule
\begin{itemize}
	\item reference to table 1: \eqref{tab:test_tab1}
	\item reference to table 2: \eqref{tab:test_tab2}
	\item reference to table 3: \eqref{tab:test_tab3_intro}
\end{itemize}
\hrule
\begin{itemize}
	\item reference to figure 1: \eqref{fig:test_fig1}
	\item reference to figure 2: \eqref{fig:test_fig2}
	\item reference to figure 3: \eqref{fig:test_fig3_intro}
\end{itemize}
\hrule

>>>>

In \cite{Batchelor} we believe.

%-------------------------------------------------------------------------------
\section{Photonic crystals}
%%
%Our contributions are as follows. We validate that the foremost wireless
%algorithm for the understanding of the lookaside buffer by O.  Moore
%\cite{cite:0} is maximally efficient. Further, we explore new real-time
%methodologies ({Hyp}), which we use to show that the little-known
%knowledge-based algorithm for the exploration of the Turing machine by Taylor
%et al. \cite{cite:0} runs in
%%
%\begin{equation}
%	\Omega (\log \log \log {n} ^ { \log \log n })
%	\label{eq:eq1}
%\end{equation}
%%
%time. This outcome might seem unexpected but has ample historical precedence.
%
%The rest of this paper is organized as follows. Primarily,  we motivate the
%need for DNS. On a similar note, we disprove the refinement of 2 bit
%architectures.  We place our work in context with the existing work in this
%area. Ultimately, we conclude.

\section{Suspension flows}

\section{Liquid-infused surfaces}

\section{Multiphase flows}

@@

%===============================================================================
\chapter{Microhydrodynamics}
%===============================================================================

%-------------------------------------------------------------------------------
\section{Stokeslet}

\section{Lubricalet}

\section{Multipole expansion}

%===============================================================================
\chapter{Numerical methods}
%===============================================================================
%
\section{The interface-correction level set/ghost fluid method}

\section{The immersed boundary method}

\section{The discrete-element lubrication/contact dynamics model}

@@

%%===============================================================================
%\chapter{Test chapter, a very very very long title to test the table of contents}
%%===============================================================================
%
%This chapter is meant for testing the correct referencing of figures, equations
%and tables.
%
%% equations
%%
%\begin{equation}
%	1 + 1 = 2
%	\label{eq:test_eq1}
%\end{equation}
%
%\begin{align}
%	2 + 2 = 4
%	\label{eq:test_eq2}
%\end{align}
%
%\begin{equation}
%	3 + 3 = 6
%	\label{eq:test_eq3_intro}
%\end{equation}
%
%% tables
%%
%\begin{table}
%	\centering
%	\begin{tabular}{c}
%		1
%	\end{tabular}
%	\caption{Test table 1}
%	\label{tab:test_tab1}
%\end{table}
%
%\begin{table}
%	\centering
%	\begin{tabular}{c}
%		2
%	\end{tabular}
%	\caption{Test table 2}
%	\label{tab:test_tab2}
%\end{table}
%
%\begin{table}
%	\centering
%	\begin{tabular}{c}
%		3
%	\end{tabular}
%	\caption{Test table 3}
%	\label{tab:test_tab3_intro}
%\end{table}
%
%% figures
%%
%\begin{figure}[h!]
%	\centering
%	test figure 1
%	\caption{Test figure 1}
%	\label{fig:test_fig1}
%\end{figure}
%
%\begin{figure}[h!]
%	\centering
%	test figure 2
%	\caption{Test figure 2}
%	\label{fig:test_fig2}
%\end{figure}
%
%\begin{figure}[h!]
%	\centering
%	test figure 3
%	\caption{Test figure 3}
%	\label{fig:test_fig3_intro}
%\end{figure}
%
%% test references
%%
%\hrule
%\begin{itemize}
%	\item reference to equation 1: \eqref{eq:test_eq1}
%	\item reference to equation 2: \eqref{eq:test_eq2}
%	\item reference to equation 3: \eqref{eq:test_eq3_intro}
%\end{itemize}
%\hrule
%\begin{itemize}
%	\item reference to table 1: \eqref{tab:test_tab1}
%	\item reference to table 2: \eqref{tab:test_tab2}
%	\item reference to table 3: \eqref{tab:test_tab3_intro}
%\end{itemize}
%\hrule
%\begin{itemize}
%	\item reference to figure 1: \eqref{fig:test_fig1}
%	\item reference to figure 2: \eqref{fig:test_fig2}
%	\item reference to figure 3: \eqref{fig:test_fig3_intro}
%\end{itemize}
%\hrule

### 2019-12-15 paper1/paper.tex
switched paper 2 with 3

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[ICLS/GFM for droplet suspensions under depletion forces] % Short title used in headlines (optional)
{%
  An efficient mass-preserving interface-correction level set/ghost fluid method
  for droplet suspensions under depletion forces% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{An efficient mass-preserving interface-correction level set/ghost fluid method
  for droplet suspensions under depletion forces} % Title for toc
%
\paperauthor[Ge, Loiseau, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Jean-Christophe Loiseau, Outi Tammisola, Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, J-Ch. Loiseau, O. Tammisola, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[J. Comput. Phys.] % Short publish info used in List Of Papers
{%
	Journal of Computational Physics%
}%
%
\papervolume{353}%
%
\papernumber{}%
%
\paperpages{435--459}%
%
\paperyear{2018}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
\todo
}%
%
\graphicspath{{paper1/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[ICLS/GFM for droplet suspensions under depletion forces] % Short title used in headlines (optional)
{%
  An efficient mass-preserving interface-correction level set/ghost fluid method
  for droplet suspensions under depletion forces% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{An efficient mass-preserving interface-correction level set/ghost fluid method
  for droplet suspensions under depletion forces} % Title for toc
%
\paperauthor[Ge, Loiseau, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Jean-Christophe Loiseau, Outi Tammisola, Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, J-Ch. Loiseau, O. Tammisola, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[J. Comput. Phys.] % Short publish info used in List Of Papers
{%
	Journal of Computational Physics%
}%
%
\papervolume{353}%
%
\papernumber{}%
%
\paperpages{435--459}%
%
\paperyear{2018}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
In this first work, I developed and implemented an interface-correction level set/ghost fluid method (\texttt{ICLS/GFM}) for high-fidelity simulations of liquid droplets in an immiscible carrier fluid. The main novelty is a global mass correction scheme, which is conceptually easy to understand, relatively straightforward to program, and fast if implemented properly. The method works best for well-resolved droplets as validated in the paper; however, extra care must be taken when applying it otherwise. In the same paper, I also formulated a hydrodynamic model for surfactant-induced depletion forces between neighbouring drops, removing the need to simulate suspending surfactants, hence further improving the computational efficiency. The overall methodology can be readily used to study droplet interactions in liquid flows, and may be extended to simulate multiphase flows in porous media in general.
}%
%
\graphicspath{{paper1/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

### 2019-12-15 paper2/paper.tex
Adding papers 3-6...
switched paper 2 with 3

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Integral representation of channel flow with interacting particles] % Short title used in healines (optional)
{%
 Integral representation of channel flow with interacting particles% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Integral representation of channel flow with interacting particles} % Title for toc
%
\paperauthor[Fouxon, Ge, Brandt, Leshansky] % Short authors used in headlines and List Of Papers
{%
  Itzhak Fouxon$^{1,2}$, Zhouyang Ge$^3$, Luca Brandt$^3$, \\Alexander Leshansky$^1$%
}%
%
\listpaperauthor{I. Fouxon, Z. Ge, L. Brandt, A. Leshansky}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Department of Chemical Engineering, Technion, Haifa 32000, Israel\\%
  $^2$ Department of Computational Science and Engineering, Yonsei University, \\Seoul 120-749, South Korea\\%
  $^3$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Phys.\ Rev.\ E] % Short publish info used in List Of Papers
{%
	Physical Review E%
}%
%
\papervolume{96}%
%
\papernumber{063110}
%
\paperpages{}%
%
\paperyear{2017}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   \todo
}%
%
\graphicspath{{paper2/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

@@

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
%
\begin{paperabstract}
	We construct a boundary integral representation for the low-Reynolds-number flow in a channel in the presence of freely-suspended particles (or droplets) of arbitrary size and shape. We demonstrate that lubrication theory holds away from the particles at horizontal distances exceeding the channel height and derive a multipole expansion of the flow which is dipolar to the leading approximation. We show that the dipole moment of an arbitrary particle is a weighted integral of the stress and the flow at the particle surface, which can be determined numerically. We introduce the equation of motion that describes hydrodynamic interactions between arbitrary, possibly different, distant particles, with interactions determined by the product of the mobility matrix and the dipole moment. Further, the problem of three identical interacting spheres initially aligned in the streamwise direction is considered and the experimentally observed ``pair exchange" phenomenon is derived analytically and confirmed numerically. For non-aligned particles, we demonstrate the formation of a configuration with one particle separating from a stable pair. Our results suggest that in a dilute initially homogenous particulate suspension flowing in a channel the particles will eventually separate into singlets and pairs.
\end{paperabstract}

@@

%------------------------------------------------------------------------------
% Bibliography
%------------------------------------------------------------------------------
%
%\clearpage
\bibliographystyle{jfm}
\bibliography{thesis}
%
\IfFileExists{paper2/paper.bbl}{\input{paper2/paper.bbl}}{}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Flow-assisted droplet assembly in a 3D microfluidic channel] % Short title used in headlines (optional)
{%
  Flow-assisted droplet assembly in a 3D microfluidic channel% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Flow-assisted droplet assembly in a 3D microfluidic channel} % Title for toc
%
\paperauthor[Ge, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Outi Tammisola, Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, O. Tammisola, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Soft Matter.] % Short publish info used in List Of Papers
{%
	Soft Matter%
}%
%
\papervolume{15}%
%
\papernumber{}%
%
\paperpages{3451--3460}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
In this paper, I performed a series of simulations, using methods developed in paper 1, to examine the droplet interaction in increasingly realistic conditions, mimicking a microfluidic experiment. The main objective was to elucidate the physical mechanism that leads to the experimentally observed droplet clustering, which had been explained by a dipolar interaction theory. Contrary to previous belief, we found that dipolar interactions alone cannot account for the fast droplet dynamics; a number of 3D effects must be included to faithfully reproduce the observation. This conclusion is supported by theoretical derivations of the Stokes flow (papers 3 and 4), implying that designing microfluidic channels to directly produce large droplet crystals remains difficult in practice.
}%
%
\graphicspath{{paper2/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

@@

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
%
\begin{paperabstract}
Self-assembly of soft matter, such as droplets or colloids, has become a promising scheme to engineer novel materials, model living matter, and explore non-equilibrium statistical mechanics. In this article, we present detailed numerical simulations of few non-Brownian droplets in various flow conditions, specifically, focusing on their self-assembly within a short distance in a three-dimensional ($3D$) microfluidic channel, cf.\
\cite{tabeling}.
%[Shen \textit{et al., Adv. Sci.}, 2016, \textbf{3}(6):1600012].
Contrary to quasi two-dimensional ($q2D$) systems, where dipolar interaction is the key mechanism for droplet rearrangement, droplets in $3D$ confinement produce much less disturbance to the underlying flow, thus experiencing weaker dipolar interactions. Using confined simple shear and Poiseuille flows as reference flows, we show that the droplet dynamics is mostly affected by the shear-induced cross-stream migration, which favors chain structures if the droplets are under an attractive depletion force. For more compact clusters, such as three droplets in a triangular shape, our results suggest that an inhomogeneous cross-sectional inflow profile is further required. Overall, the accelerated self-assembly of a small-size droplet cluster results from the combined effects of strong depletion forces, confinement-mediated shear alignments, and fine-tuned inflow conditions. The deterministic nature of the flow-assisted self-assembly implies the possibility of large throughputs, though calibration of all different effects \xx{to directly produce large droplet crystals is generally difficult}.
\end{paperabstract}

@@

%------------------------------------------------------------------------------
% Bibliography
%------------------------------------------------------------------------------
%
\clearpage
\bibliographystyle{jfm}
\bibliography{thesis}
%
\IfFileExists{paper2/paper.bbl}{\input{paper2/paper.bbl}}{}
